### 2018-09-08 sections/conclusion.tex
Implemented remaining replies to CDS comments from Jason Nielsen

A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions measured so far.

>>>>

A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$ respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$ respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions measured so far.

### 2018-09-08 sections/data_presel.tex
Implemented remaining replies to CDS comments from Jason Nielsen

In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected charged light lepton is required to match, with $\Delta R < 0.15$, the lepton triggering the event and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected charged light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both ditau channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.

>>>>

In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected charged light lepton is required to match, with $\Delta R < 0.15$, the lepton triggering the event and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected charged light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both $\Htautau$ search channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.

### 2018-09-08 sections/introduction.tex
little changes I forgot to plug in
Implemented remaining replies to CDS comments from Jason Nielsen

Following the observation of a Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
%looking for deviations from the Standard Model (SM) predictions.  
An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions would manifest themselves as FCNC top-quark decays, $t\to H q$.  
In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and even suppressed at higher orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk}, or supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}. In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced relative to the SM prediction in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
See Ref.~\cite{Agashe:2013hma} for a review.
%\textbf{Update a bit above paragraph mentioning more recent models.}

@@

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
The searches presented in this paper are focussed on fermionic decay modes.
Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, 
which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 
of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets.

>>>>

Following the observation of a Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
%looking for deviations from the Standard Model (SM) predictions.  
An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to H q$.  
In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and even suppressed at higher orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk}, or supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}. In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced relative to the SM prediction in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
%See Ref.~\cite{Agashe:2013hma} for a review.
%\textbf{Update a bit above paragraph mentioning more recent models.}

@@

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
The searches presented in this paper are focussed on fermionic decay modes.
Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, 
which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 
of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets. 
The latter requirement is aimed at selecting events with a hadronically-decaying $W$ boson, since this allows an improved reconstruction of the
event kinematics.

### 2018-09-08 sections/signal_background_modeling.tex
Implemented remaining replies to CDS comments from Jason Nielsen

Samples of simulated $\ttbar \to WbHq$ events are generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial and final state radiation, referred to as the ``tune'', is used.
The signal sample is normalised to the same total cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).

@@

%The $\Hbb$ search requires a more sophisticated treatment of the $\ttbar$ background. 
The $\ttbar$ background selected by the $\Hbb$ search is enriched in $\ttbar$+heavy-flavour production, and thus requires a more sophisticated 
treatment than provided by the nominal $\ttbar$ sample. 
%The large and complex $\ttbar$ background selected by the $\Hbb$ search requires a more sophisticated treatment than provided by the nominal $\ttbar$ sample. 
Therefore, the simulated $\ttbar$ events are categorised depending 
on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system (see Ref.~\cite{Aaboud:2017rss} for details).
Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for ``heavy flavour''.
The remaining events are labelled as $\ttbar$+light-jets events, including those with no additional jets. 
A finer categorisation of \ttbin\ events is considered for the purpose of applying further corrections and
assigning systematic uncertainties associated with the modelling of heavy-flavour production in different event topologies~\cite{Aaboud:2017rss}.
In particular, the \ttbin\ events are reweighted to an NLO prediction in the four-flavour (4F) scheme 
of \ttbin\ production including parton showering~\cite{Cascioli:2013era}, based on {\ShOLlong}~\cite{Gleisberg:2008ta, Cascioli:2011va} (referred to as {\ShOL} 
in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
while preserving the nominal \ttbin\ cross section of the nominal $\ttbar$ sample. 
%This reweighting is applied to the alternative $\ttbar$ samples as well.
This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties (see Section~\ref{sec:syst_bkgmodeling}).

>>>>

Samples of simulated $\ttbar \to WbHq$ events are generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial and final state radiation, referred to as the ``tune'', is used.
The signal sample is normalised to the same total cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).

@@

%The $\Hbb$ search requires a more sophisticated treatment of the $\ttbar$ background. 
The $\ttbar$ background selected by the $\Hbb$ search is enriched in $\ttbar$+heavy-flavour production, and thus requires a more sophisticated 
treatment than provided by the nominal $\ttbar$ sample. 
%The large and complex $\ttbar$ background selected by the $\Hbb$ search requires a more sophisticated treatment than provided by the nominal $\ttbar$ sample. 
Therefore, the simulated $\ttbar$ events are categorised depending 
on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system (see Ref.~\cite{Aaboud:2017rss} for details).
Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for ``heavy flavour''.
The remaining events are labelled as $\ttbar$+light-jets events, including those with no additional jets. 
A finer categorisation of \ttbin\ events is considered for the purpose of applying further corrections and
assigning systematic uncertainties associated with the modelling of heavy-flavour production in different event topologies~\cite{Aaboud:2017rss}.
In particular, the \ttbin\ events are reweighted to an NLO prediction in the four-flavour (4F) scheme 
of \ttbin\ production including parton showering~\cite{Cascioli:2013era}, based on {\ShOLlong}~\cite{Gleisberg:2008ta, Cascioli:2011va} (referred to as {\ShOL} 
in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
while preserving the \ttbin\ cross section of the nominal $\ttbar$ sample. 
%This reweighting is applied to the alternative $\ttbar$ samples as well.
This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties (see Section~\ref{sec:syst_bkgmodeling}).
